Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
minor

% COMMENTING PREVIOUS WORK AND DEFINITIONS
\iffalse
\subsectionDefinitions}
A pattern, or a patch, is a beat-chroma pattern taken from an actual song.
A codeword (sometimes just code) is similar to a pattern, but is the result 
of the clustering
algorithm and most likely does not come from an actual song.
Distortion is our measure of distance between a pattern and a code
(or between two patterns, see equation \ref{eq:dist} in Section 
\ref{sec:experiments}).

\subsection{Previous Work}\label{sec:prevwork}
Our work can be seen as an extension of the \textit{Shingles} idea
described by Casey and Slaney \cite{Casey2006,Casey2007,Casey2008}.
The two main differences are the clustering framework and the use of
beats and bars to select the position of the \textit{Shingles}.

Casey and Slaney \cite{Casey2006} use LSH \cite{Datar2004} to perform
fast approximate nearest neighbor search. Their implementation is E$^2$LSH
\cite{E2LSH}. This package can efficiently handle about $50$K or $100$K
vectors of size $200$. Even with a better implementation, the LSH
model still has some scaling problem. A large portion of the data
must be known to decide how many projections to use, and what guarantee
of finding the nearest neighbor it can provides. Also, we could fix the
number of projections and consider as clusters all the elements that
fall into the same bin. However, this does not give us a centroid, a
typical pattern representing that cluster.
\fi

@@

\section{Experiments}\label{sec:experiments}
In this section we present different clustering experiments. We introduce
our training data and our main testing data. Some detailed settings
of our algorithm are also provided. Then, we answer some common questions
about any clustering algorithms, for instance 
``how the number of codes affect the distortion''
and ``how many learning samples should we use''.
% Note that we will present two additional experiments in 
% Section \ref{sec:exps2}.

@@

% REMOVING THE FOLLOWING SUBSECTION ON RATE - DISTORTION
\iffalse
\subsection{Music Randomness}\label{ssec:random}
It will not surprise any reader, music is not random. This fact should
become apparent in our experiments in the following way. Information
theory tells us that if the signal to encode doubles, we need to square
the size of the codebook to encode it with the same distortion.

To help the intuition, here is an example. Imagine a binary array of 
length $1$. We need two
codes to encode perfectly: $(0)$ and $(1)$. If the binary array is now of
length $2$, we now need four codes: $(0,0)$, $(0,1)$, $(1,1)$ and $(1,0)$.

Since music is not random, we expect that squaring the codebook when the
pattern size doubles will rather give improved results than constant ones.
See Figure \ref{fig:size_pattern}.

% see generate_expo_codes_curves.py to generate the following figure:
\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{codesize_patternsize}
\end{center}
\caption{\small{
Experiment on squaring the codebook size when the pattern size doubles.
Each line represent $4$ codebook sizes: $2$, $4$, $16$ and $256$.
The pattern size range from $1$ for $1/4$ of a bar to $32$ for $8$ bars.
If everything was random, each of these lines should be flat. The training
size was fixed to $128$K samples.
}}
\label{fig:size_pattern}
\end{figure}
\fi

>>>>

@@

\section{Experiments}\label{sec:experiments}
In this section we present different clustering experiments. We introduce
our training data and our main testing data. Some detailed settings
of our algorithm are also provided. As for any clustering algorithm, we
measure the influence of the number of codewords and the training set size.

@@
